\begin{center}
\thispagestyle{empty}
\vspace{2cm}
\LARGE{\textbf{ABSTRACT}}\\[1.0cm]
\end{center}
\thispagestyle{empty}
In today's fast-paced digital environment, the importance of accessible and engaging online learning platforms for learning facilitators cannot be underestimated. This content introduces "Query Quest - Edu", an interactive online learning program developed using HTML, CSS, JavaScript and PHP technologies.\newline

'Query Quest - Edu' stands as an educational beacon providing a variety of educational video content covering a wide range of topics including but not limited to coding, business, design, marketing, music, photography, software and science. Thanks to carefully designed playlists and seamless navigation, students have access to a variety of educational programs tailored to their personal interests and learning expectations.\newline

The spirit of "Query Quest - Edu" is based on the goal of encouraging curiosity, encouraging discovery and encouraging users to seek knowledge. By offering a recognized and user-friendly educational ecosystem, "Query Quest - Edu" actively promotes a culture of collaboration and collaboration, thus enabling deep and meaningful learning for students of all backgrounds and skill levels.\newline

The theme of the name "Query Quest - Edu" summarizes the platform's unwavering commitment to supporting curiosity-driven educational adventures. Based on a commitment to continuous improvement and innovation, "Query Quest - Edu" strives to become an online learning community that encourages students to participate in the changing world, learning science that holds the promise of discovery, inspiration and personal growth.\newline

This content provides a general introduction to the overall vision and principles of "Query Quest - Edu" regarding its immense potential to revolutionize online education and help students around the world.

 \vspace{0.5cm}


