\section{About Project }
\subsection{Title}
\paragraph{}The title of our project is \textbf{ “Query Quest-  Edu”}
\subsection{Domain}
\paragraph{}Online Education/E-Learning Platform
\subsection{Aim }
\paragraph{}Query Quest - Edu's overall goal is to disrupt the traditional education system to bridge the gap between students and provide access to quality education in the digital age. Query Quest - Edu is committed to providing free access to knowledge and helping people from diverse backgrounds begin educational transformation by creating a powerful and inclusive online platform.

\paragraph{}Query Quest - Edu specifically aims to achieve the following goals:

\begin{itemize}
\item Provide Usability: Query Quest - Edu aims to achieve this by providing an easily accessible online platform that can be accessed from anywhere, anytime. complete any educational program. The platform eliminates geographical and financial barriers, allowing international students to access quality educational content.

\item Encouraging Participation: The core of Query Quest - Edu's mission is to create a strong and interactive learning community. Through features such as curated playlists, user-generated content, and interactive learning modules, the platform encourages interaction and collaboration between students, fostering a culture of knowledge sharing and peer support.

\item Personalized Learning: Query Quest - Edu recognizes that each student is unique and therefore strives to provide personalized learning tailored to individual interests, preferences and standards. Leveraging data-driven insights and adaptive learning algorithms, the platform provides customized recommendations and learning methods to optimize each user's learning experience.

\item Supporting Lifelong Learning: Query Quest - Edu is committed to promoting a love of lifelong learning by providing a variety of courses that meet the needs of students of all ages, ages and skill levels. Constantly expanding and constantly updating its content library, the platform aims to arouse curiosity in users, encourage intellectual curiosity and stimulate brain development.
\end{itemize} 
More importantly, Query Quest - Edu wants to be more than just an online education; It aims to be a social change, helping people realize their potential, find their interests and create a future for themselves and future generations. in the future.

\newpage


\subsection{Objective}
\begin{itemize}
\item Enhanced Accessibility: Query Quest - Edu aims to provide quality education to a wide range of students regardless of location, economic status or physical limitations. By providing an online platform that can be accessed from any internet device, the aim is to make the courses accessible to everyone with an internet connection.

\item Encouraging Collaboration: Query Quest - Edu is committed to fostering collaboration by providing interactive learning experiences, collaboration tools, and community forums to enable collaboration with users. The goal is to create a strong learning community where students can connect with their peers, share knowledge, and collaborate on projects.

\item Personalized Learning: Query Quest - Edu is committed to providing personalized learning to all users based on their personal interests, preferences and learning styles. By analyzing data and machine learning algorithms, the aim is to provide appropriate recommendations, learning modifications and personalized recommendations to improve the learning experience.

\item Promoting lifelong learning: Query Quest - Edu aims to foster a culture of lifelong learning by providing a variety of educational content that meets the needs of students of all ages and skill levels. The goal is to spark curiosity, encourage intellectual development, and encourage a love of learning that goes beyond art.

\item Empowering Educators: Query Quest - Edu recognizes the critical role of educators in enhancing learning and aims to empower them with tools, resources and development efforts. The aim is to support teachers in creating an engaging and effective learning experience for students, ultimately improving the quality of learning through the platform.
   
\end{itemize} 
\newpage
\subsection{Problem Statement }

\paragraph{} The education system is currently grappling with issues that impede access to quality education and hinder international students' learning. These issues include:
\begin{itemize}
\item Limited Access: Many people, especially those living in remote or underserved areas, cannot access quality education due to geographic restrictions, usage restrictions, or financial constraints. This lack of education leads to educational inequality and widens the gap between the privileged and the poor.

\item Engagement Issues: Traditional education systems often disable students, leaving them less engaged, less engaged, and less motivated. Exaggerated learning, exaggerated curriculum, and lack of interactive learning can make students disinterested and inhibit the development of positive thinking.

\item One-size-fits-all approach: Traditional education systems follow a standard, one-size-fits-all approach. -A one-size-fits-all approach fails to meet the student's diverse learning needs, preferences, and abilities. This integrated approach does not accommodate different learning styles, challenges, and interests, resulting in a learning environment that may not meet the needs of all students.

\item Teacher Support: Teachers often struggle to convey knowledge, self-manage, provide timely feedback, and meet students' individual needs. The girl in the older class. Limited resources, high teacher-student ratios, and inadequate infrastructure can inhibit teacher effectiveness and impact student learning.

\item There is no way to learn forever: The main focus of technical education is the transfer of knowledge and skills within a limited period of time. Pioneers often overlook the importance of continuous learning and skill development. As a result, people will have difficulty adapting to rapid changes in the market, technological changes and changing social needs, and the work they do will become good and useless.
\end{itemize} 

 \paragraph{}According to these challenges, there is an urgent need for new solutions that use technology, personal learning and the integration of the learning environment to meet the different needs of students and teachers. Query Quest - Edu strives to solve these problems by providing an accessible, engaging and personalized online learning platform that enables students to realize their potential and pursue lifelong learning.




