\section{Literature Survey}
\subsection{Literature Survey}
\paragraph{}Query Quest - Edu's research database provides research, publications and research related to online education, app design, personalized learning and access to education. The purpose of this chapter is to provide an overview of the current state of online education and to identify the main issues, challenges and opportunities related to the development of Query Quest - Edu.


\paragraph{}The literature review will examine the following topics: 

\begin{itemize}
\item Online Learning Platforms: A study of existing online learning platforms and their features, performance and effectiveness of educational support.

\item User Experience Design: Learn about user interface design principles, usability, and user experience design in online learning.

\item Personalized Learning: Identification of personalized learning strategies, emerging learning technologies and their effects on student motivation, participation and learning.

\item Accessibility in Education: Explore accessibility standards, guidelines, and best practices for creating online education for people with disabilities.
\end{itemize} 

\paragraph{}Through the results of comprehensive data analysis, Query Quest - Edu aims to gain insight, inform design decisions and identify areas for development, innovation and development to create user-friendly, efficient and inclusive online learning platforms.



\subsection{Conclusion}
\paragraph{}Case studies demonstrate the diversity of online learning platforms and highlight the importance of user-friendly design, personalized learning and accessibility. Insights from existing studies guide the development of Query Quest - Edu, ensuring that user involvement, identity, and engagement are important. Query Quest - Edu aims to use these findings to create a new online education that meets the needs of global students, encouraging motivation, memory and learning, and well-being in a practical and productive environment.

.

\vspace{9.5cm}




