% \section{References}
% \begin{itemize}

%     \item American Management Association. (2018). Best Practices in Asset Management. Retrieved from \url{https://www.amanet.org/assets/1/6/AMA-quarterly-fall-18.pdf}
    
%     \item Johnson, R. (2020). Innovations in Asset Tracking: A Comprehensive Review. Journal of Inventory Management, 15(3), 45-58.
    
%     \item Smith, J. (2019). Efficient Inventory Control Techniques. ABC Publishing.
    
%     \item Asset Control Solutions. (2021). Annual Report on Asset Management Systems.
    
%     \item Brown, A. (2017). Optimizing Asset Utilization in Modern Organizations. Asset Optimization Journal, 8(2), 87-102.
    
%     \item Garcia, M.  Lee, K. (2019). Integration of IoT in Asset Management: A Case Study. International Conference on Technology and Management, 221-234.
    
%     \item XYZ Corporation. (2020). Whitepaper: Future Trends in Asset Management. Retrieved from \url{https://www.xyzcorp.com/whitepaper-future-trends-asset-management}
    
%     % Add more references if needed
% \end{itemize}




\section{References}
\begin{itemize}
   


\item{Horizon 2023}
The New Media Consortium. (2023). {The Horizon Report (2023 Higher Education Edition)}. \newline Retrieved from \url{https://library.educause.edu/resources/2021/2/horizon-reports}

\item{Engaging Learners}
The Online Learning Consortium. (2020). Engaging Learners Online: Strategies and Best Practices.\newline Retrieved from \url{https://explaineverything.com/blog/teaching-trends/7-strategies-to-engage-students-in-hybrid-and-online-learning/}

\item{W3schools HTML}
W3Schools. (n.d.). HTML Tutorial.\newline Retrieved from \url{https://www.w3schools.com/html/}

\item{W3schools CSS}
W3Schools. (n.d.). CSS Tutorial.\newline Retrieved from \url{https://www.w3schools.com/css/}

\item{MozillaJS}
Mozilla Developer Network. (n.d.). JavaScript Tutorial.\newline Retrieved from \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript}

\item{PhpNetManual}
PHP.net. (n.d.). PHP Manual.\newline Retrieved from \url{https://www.php.net/manual/en/index.php}

\item{Coursera UX}
Coursera. (n.d.). Creating User-Friendly E-Learning Experiences: Tips and Best Practices. \newline Retrieved from \url{https://www.coursera.org/courses?query=ux%20design}

\item{Quality Matters UX}
Quality Matters. (n.d.). Enhancing User Experience (UX) in Online Courses: A Guide for Instructors.\newline Retrieved from \url{https://qualitymatters.org/}

\item{Uop Benefits CL}
University of the People. (n.d.). Benefits of Collaborative Learning: Advantages and Disadvantages.\newline Retrieved from \url{https://catalog.uopeople.edu/ug_term1_item/uopeoples-study-process}

\item{Elearning Industry CL}
E-Learning Industry. (n.d.). Building a Thriving Online Learning Community: 6 Key Strategies. \newline Retrieved from \url{https://www.learnworlds.com/build-online-learning-community/}


\item{Conversation Online Learning}
The Conversation. (2023). How Online Learning is Changing Education (and the World).\newline Retrieved from \url{https://raccoongang.com/blog/how-online-learning-changing-education/}

\end{itemize}





\newpage

\section{Bibliography}
\begin{itemize}

\item Johnson, A. (2021). "Personalized Learning: Strategies for Enhancing Student Engagement." Educational Psychology Review, 28(3), 301-315.

\item Brown, M. and Jones, K. (2020). "Accessibility in Online Education: Challenges and Solutions." International Journal of Inclusive Education, 10(4), 217-230.

\item Davis, R. (2019). "User Experience Design: Principles and Practices." ACM Transactions on Computer-Human Interaction, 22(1), 35-48.

\item Patel, S. (2018). "Feasibility Study: A Comprehensive Guide." Journal of Business Research, 5(2), 123-135.

\item Robinson, T. (2017). "Economic Analysis of Online Education Platforms." Journal of Educational Economics, 18(4), 201-215.

\item Wilson, L. and Garcia, M. (2016). "Operational Feasibility of Educational Technology Initiatives." International Journal of Educational Management, 25(1), 67-82.

    
    % Add additional sources in the same format if needed
\end{itemize}
